Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2024-01-03 manuscript_revised.RMD
working on revision

**Purpose:** Resistance training-induced skeletal muscle hypertrophy seems to depend on ribosome biogenesis and content. High glucose treatment may augment ribosomal biogenesis, as evident from *in vitro* studies, and may thus act to potentiate resistance training-induced adaptations *in vivo*. However, this remains largely unexplored.

@@

Total protein was extracted using the Minute Total Protein Extraction Kit for Muscles (Invent Biotechnology), according to the manufacturer's protocol, optimised for our lab. Wet muscle was freeze-dried for 24 hours and dissected before extraction. The tissue was homogenised with a plastic rod in 80 mg protein extraction powder (Invent Biotechnology) and 100 ul ice-cold cell lysis buffer (Denaturing Buffer, Invent Biotechnology), and centrifuged at 19 000 g for 1 minute. The supernatant was divided into aliquots to run samples in duplicates, and total protein concentrations were determined in a 1:10 dilution (Pierce Detergent Compatible Bradford Assay Reagent, Thermo Fisher Scientific, Oslo, Norway). The protein samples were diluted to a concentration of 1.5 µg µl^−1^ with lysis buffer and 4X Laemmli sample buffer (Bio-Rad Laboratories AB, Oslo, Norway) containing 2-mercaptoethanol. All protein samples were incubated at 95°C and stored at -20°C until further analysis. The protein samples (20.25 µg total protein) were separated at 250V on 4-20% Tris-Glycine gels (Bio-Rad Laboratories) for 50 minutes and then transferred to PVDF membranes with wet transfer at 300 mA for 3 hours. Both gel electrophoresis and protein transfer were performed at 4°C. Following the wet transfer, membranes were stained with a reversible total protein stain (Thermo Fisher Scientific) and then blocked for 1 hour at room temp with a blocking buffer of Tris-buffered saline (TBS; 20 mM Tris, 150 mM NaCl) with 5% non-fat dry milk and 0.1% Tween-20. Primary and secondary antibodies were purchased from Santa Cruz Biotechnology (Texas, USA): UBF, UBF F-9, sc-13125; rpS6, Ribosomal protein S6 C-8, sc-74459; and Thermo Fisher Scientific (Oslo, Norway): c-Myc, 9E10; goat anti-mouse (for c-Myc), goat anti-mouse IgG1 (y1) horseradish peroxidase conjugate; and anti-mouse (anti-mouse IgG1 horseradish peroxidase conjugate). Antibodies were diluted in blocking buffer to concentrations corresponding to 1:25 000 (UBF, rpS6) and 1:5000 (c-Myc).

>>>>

**Purpose:** Resistance training-induced skeletal muscle hypertrophy seems to depend on ribosome biogenesis and content. High glucose treatment may augment ribosomal biogenesis, as evident from *in vitro* studies, and may thus act to potentiate resistance training-induced adaptations *in vivo*. This was investigated with the main outcomes being total RNA and ribosomal RNA abundances, as well as relevant transcriptional or translational regulators (c-Myc/UBF/rpS6) to further describe the relationship between these regulators and ribosome biogenesis in human skeletal muscle tissue.

@@

Total protein was extracted using the Minute Total Protein Extraction Kit for Muscles (Invent Biotechnology), according to the manufacturer's protocol, optimised for our lab. Wet muscle was freeze-dried for 24 hours and dissected before extraction. The tissue was homogenised with a plastic rod in 80 mg protein extraction powder (Invent Biotechnology) and 100 ul ice-cold cell lysis buffer (Denaturing Buffer, Invent Biotechnology), and centrifuged at 19 000 g for 1 minute. The supernatant was divided into aliquots to run samples in duplicates, and total protein concentrations were determined in a 1:10 dilution (Pierce Detergent Compatible Bradford Assay Reagent, Thermo Fisher Scientific, Oslo, Norway). The protein samples were diluted to a concentration of 1.5 µg µl^−1^ with lysis buffer and 4X Laemmli sample buffer (Bio-Rad Laboratories AB, Oslo, Norway) containing 2-mercaptoethanol. All protein samples were incubated at 95°C and stored at -20°C until further analysis. The protein samples (20.25 µg total protein) were separated at 250V on 4-20% Tris-Glycine gels (Bio-Rad Laboratories) for 50 minutes and then transferred to PVDF membranes with wet transfer at 300 mA for 3 hours. Both gel electrophoresis and protein transfer were performed at 4°C. Following the wet transfer, membranes were stained with a reversible total protein stain (Thermo Fisher Scientific) and then blocked for 1 hour at room temp with a blocking buffer of Tris-buffered saline (TBS; 20 mM Tris, 150 mM NaCl) with 5% non-fat dry milk and 0.1% Tween-20. Primary and secondary antibodies were purchased from Santa Cruz Biotechnology (Texas, USA): UBF, UBF F-9, sc-13125; rpS6, Ribosomal protein S6 C-8, sc-74459; and Thermo Fisher Scientific (Oslo, Norway): c-Myc, 9E10; goat anti-mouse (for c-Myc), goat anti-mouse IgG1 (y1) horseradish peroxidase conjugate; and anti-mouse (anti-mouse IgG1 horseradish peroxidase conjugate). <!-- Reviewer comment: 25,000 dilution for primary seems quite diluted. Is the dilution is correct? Revision: Antibodies were diluted in blocking buffer to concentrations corresponding to 1:500 (UBF and rpS6, primary), 1:2000 (c-Myc, primary), 1:5000 (c-Myc, secondary) and 1:25 000 (UBF, rpS6, secondary).-->
